Validation of Visual Statistical Inference, with Application to Linear Models

### 2012-04-26 paper_jasa.tex
small changes

\blue{
\paragraph{Subject-specific Power}
Probability to reject null hypothesis is power. This is intricately related to the probability to identify the data plot from the lineup. We need to address the problematic of individual specific abilities in identifying the data plot
}. 
\red{HH: need to cite some literature from cognitive science here}

\blue{Let $X_{j\ell} \sim B_{1, \pi_{j\ell}}$ be the random variable, with $X_{j\ell}= 1$, if  subject $j$ correctly identifies the data plot from lineup $\ell$, and 0 otherwise.
We can model $\pi_{j\ell}$ with a logistic regression with subject specific random effects as:
\[
\text{logit } \pi_{j\ell} = X_\ell \beta + Z u_j,  
\]
where $X_\ell$ is a matrix of fixed effects with parameter vector $\beta$ corresponding to lineup $\ell$ and $u \sim MVN(0, \sigma_u I)$  is a vector of random variables $j = 1, ..., J$.
}

>>>>

\blue{
\paragraph{Subject-specific power}
Probability to reject null hypothesis is power. This is intricately related to the probability to identify the data plot from the lineup. We need to address the problematic of individual specific abilities in identifying the data plot
}. 
\red{HH: need to cite some literature from cognitive science here}

\blue{Let $X_{j\ell} \sim B_{1, \pi_{j\ell}}$ be the random variable, with $X_{j\ell}= 1$, if  subject $j$ correctly identifies the data plot from lineup $\ell$, and 0 otherwise.
We can model $\pi_{j\ell}$ with a logistic regression with subject specific random effects as:
\[
\text{logit } \pi_{j\ell} = X_\ell \beta + Z u_j,  
\]
where $X_\ell$ is a matrix of fixed effects with parameter vector $\beta$ corresponding to lineup $\ell$ and $u \sim MVN(0, \sigma_u I)$  is a vector of random variables $j = 1, ..., N_\ell$ for each of $N_\ell$ subjects presented with lineup $\ell$.
}
